### 2013-09-29 tex/scam/nips13/appendix.tex
first init

We start with a lemma similar to Lemma~\ref{lem:general_int_reduction} and whose proofs are identical.

\begin{lemma}
\label{lem:int_reduction}
Let $F$ be a product distribution on $C=[0,1]^s$ with density function $p$. Let $f: C \rightarrow \R$ be a convex function. Suppose that $\E f(X) = 0$.

@@

Then $f^*_k(x_k) = \E[ f(X) \given x_k]$.
\end{lemma}

@@

Fix $x_k$, we will show that the value $\E[ f(X) | x_k]$, for all $x_k$,  uniquely minimizes 
\[
\min_{ f_k(x_k) } \int_{\mathbf{x}_{-k}} p(x) | f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) - f_k (x_k)|^2 d \mathbf{x}_{-k}.
\]
If this is true, then the function $x_k \mapsto \E[ f(X) \given x_k]$ is the unique $f^*_k(x_k)$ that minimizes the expected square error.

Take the derivative with respect to the value $f_k(x_k)$ and set it equal to zero, we get that
\begin{align*}
\int_{\mathbf{x}_{-k}} p(\mathbf{x}) f_k(x_k) d \mathbf{x}_{-k} &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) ) d \mathbf{x}_{-k} \\  
   p(x_k) f_k(x_k) &= p(x_k) \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) ) d \mathbf{x}_{-k} \\
f_k(x_k) &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f(\mathbf{x}) d \mathbf{x}_{-k} 
 \end{align*}
Where the second line follows because $p(\mathbf{x}) = \prod_k p(x_k)$ by product distribution assumption. The third line follows because $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f^*_{k'}(x_{k'}) d\mathbf{x}_{-k} = 0$ for all $k' \neq k$ by the constraint that $\E[f^*_{k'}(X_{k'})] = 0$.

The square error objective is strongly convex. The second derivative with respect to $f_k(x_k)$ is $2 p(x_k)$, which is always positive under the assumption that $p$ is positive. Therefore, the solution $f^*_k(x_k) = \E[ f(X) \given x_k ]$ is unique.

Now, we verify that as a function of $x_k$, $\E[ f(X) | x_k]$ has mean zero and is convex. The former is true because $\E f(X) = 0$; the latter is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k}) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex.

@@

 \begin{proposition}
Let $F$ be a product distribution supported on $C=[0,1]^s$ with positive density $p > 0$. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.

@@

By the assumption that , we know that, for all $x_k$,
\begin{align*}
p(x_k) \E[ f(X) | x_k ] &=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} =0
\end{align*}

@@

Let $\mathcal{C}[s,b,B,L]$ be the set of additive functions with $s$ components each of which is in $\mathcal{C}[b,B,L]$. 
\[
\mathcal{C}[s,b,B,L] \coloneqq \{ f : \R^s \rightarrow \R \,:\, f = \sum_{k=1}^s f_k(x_k), \, f_k \in \mathcal{C}[b,B,L] \}
\]

@@

Let $\mathcal{C}_\epsilon[s,b,B,L]$ be an $\epsilon$-cover of $\mathcal{C}[s,b,B,L]$.

For all $f \in \mathcal{C}^s[b,B,L]$,
\[
\hat{R}_s(f) - R_s(f) = \hat{R}_s(f) - \hat{R}_s(f') + \hat{R}_s(f') - R_s(f') + R_s(f') - R_s(f)
\]
where $f' \in \mathcal{C}_\epsilon[s,b,B,L]$ and $\| f - f' \|_\infty \leq \epsilon$.\\

Step 1. We first bound $\hat{R}_s(f) - \hat{R}_s(f')$.

>>>>

We start with a lemma similar, and whose proof is identical to Lemma~\ref{lem:general_int_reduction}.

\begin{lemma}
\label{lem:int_reduction}
Let $\mu$ be a probability measure on $C=[0,1]^s$. Let $f: C \rightarrow \R$ be a convex function, twice differentiable. Suppose that $\E f(X) = 0$.

@@

Then $f^*_k(x_k) = \E[ f(X) | x_k]$.
\end{lemma}

@@

Fix $x_k$, we will show that the value $\E[ f(X) | x_k]$ minimizes 
\[
\min_{ f_k(x_k) } \int_{\mathbf{x}_{-k}} p(x) | f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) - f_k (x_k)|^2 d \mathbf{x}_{-k}.
\]

Take the derivative with respect to $f_k(x_k)$ and set it equal to zero, we get that
\begin{align*}
\int_{\mathbf{x}_{-k}} p(\mathbf{x}) f_k(x_k) d \mathbf{x}_{-k} &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}) ( f(\mathbf{x}) - \sum_{k' \neq k} f^*_{k'} (x_{k'}) ) d \mathbf{x}_{-k}  
p(x_k) f_k(x_k) &= \int_{\mathbf{x}_{-k}} p(\mathbf{x}) f(\mathbf{x}) d \mathbf{x}_{-k} 
 \end{align*}

Now, we verify that as a function of $x_k$, $\E[ f(X) | x_k]$ has mean zero and is convex. The former is true because $\E f(X) = 0$; the latter is true because for every $\mathbf{x}_{-k}$, $f(x_k, \mathbf{x}_{-k})$ is a convex function with respect to $x_k$ and therefore, $\int_{x_{-k}} p(\mathbf{x}|x_k) f(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}$ is still convex.

@@

 \begin{proposition}
Let $p$ be a product probability distribution supported and positive on $C=[0,1]^s$ so that $X_1,...,X_s$ are all independent. Let $f: C \rightarrow \R$ be a convex function, twice differentiable.

@@

By the assumption that $p$ is a product measure, we know that, for all $x_k$,
\begin{align*}
p(x_k) \E[ f(X) | x_k ] &= \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}} \,|\, x_k) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} \\
		&=  \int_{\mathbf{x}_{-k}} p(\mathbf{x_{-k}}) f(x_k,\mathbf{x}_{-k}) d \mathbf{x}_{-k} =0
\end{align*}

@@

Let $\mathcal{C}^s[b,B,L]$ be the set of additive functions with $s$ components each of which is in $\mathcal{C}[b,B,L]$. 
\[
\mathcal{C}^s[b,B,L] \coloneqq \{ f : \R^s \rightarrow \R \,:\, f = \sum_{k=1}^s f_k(x_k), \, f_k \in \mathcal{C}[b,B,L] \}
\]

@@

Let $\mathcal{C}_0^{s}[b,B,L]$ be an $\epsilon$-cover of $\mathcal{C}^s[b,B,L]$.

For all $f \in \mathcal{C}^s[b,B,L]$,
\[
\hat{R}_s(f) - R_s(f) = \hat{R}_s(f) - \hat{R}_s(f') + \hat{R}_s(f') - R_s(f') + R_s(f') - R_s(f)
\]
where $f' \in \mathcal{C}_0^s[b,B,L]$ and $\| f - f' \|_\infty \leq \epsilon$.

We first bound $\hat{R}_s(f) - \hat{R}_s(f')$.

### 2013-09-29 tex/scam/result.tex
first init

\textbf{Setting:}
\begin{packed_enum}
\item Let $Y' = f_0(X) + \epsilon$ where $f_0$ is the true function and $\epsilon$ is noise.  Given $n$ samples $Y'^{(1)},...,Y'^{(n)}$, we input into our optimization $Y = Y' - \bar{Y}'$.
\item Let $\mathcal{X} = [-b, b]^p$. Let $\mathcal{P}$ be a distribution on $\mathcal{X}$. Let $X^{(1)},..., X^{(n)} $ be independent samples from $\mathcal{P}$. 
\item Let $S \subset \{1,...,p\}$ denote the set of relevant variables, that is, $f_0(X) = f_0(X_S)$ and let $s \coloneqq |S|$.
\end{packed_enum}

\textbf{Assumptions:}
\begin{packed_enum}
\item[A1] Suppose that $X_S, X_{S^c}$ are independent.
\item[A1'] Suppose A1 is true and $\{ X_k \}_{k \in S}$ are all independent. 
\item[A2] Suppose that $\|f_0\|_\infty \leq B$.
\item[A2'] Suppose that A2 is true and $f_0$ is convex and $L$-$Lipschitz$.
\item[A3] Suppose $\epsilon$ is mean-zero subgaussian, independent of $X$, with subgaussian scale $\sigma$.
\end{packed_enum}

@@

\subsection{Reformulation}

Let $x_{s(1)} ,..., x_{s(n)}$ be the $n$ samples arranged from small to large. Define $\hat{\beta}_{s1}$ as $\frac{\hat{f}_s(x_{s(2)}) - \hat{f}_s(x_{s(1)})}{x_{s(2)} - x_{s(1)}}$.\\

Then  
\begin{align*}
\hat{f}_s(x_{s(1)}) &= \hat{f}_s(x_{s(1)})  \qquad \trm{ constrained by centering}\\
\hat{f}_s(x_{s(2)}) &= \hat{f}_s(x_{s(1)}) + \hat{\beta}_{s1} (x_{s(2)}-x_{s(1)} )\\
\hat{f}_s(x_{s(t)}) &= \hat{f}_s(x_{s(1)}) + \sum_{t' = 1}^{t-1} \hat{\beta}_{s t'} ( x_{s (t'+1)} - x_{s (t')}) 
\end{align*}

We thus define the notation $\hat{f}_s(x_{si}) = c_s + \hat{\beta}_s^\tran D_{si}$ where $D_{si} \in \R^{n-1}$, and is a vector
\[
D_{si} = [ x_{s(2)} - x_{s(1)}, x_{s(3)} - x_{s(2)}, ..., x_{s(t)} - x_{s(t-1)}, 0, ..., 0] \qquad \trm{ where } t = order(i)
\]

And we have the constraint that $\sum_{i=1}^n \hat{f}_s(x_{si}) = n c_s + \sum_{i=1}^n \hat{\beta}_s^\tran D_{si} = 0$, therefore, $c_s = - \left( \frac{1}{n} \sum_{i=1}^n  D_{si} \right)^\tran \hat{\beta}_s$.

\textbf{Some additional transformation.} Let's define $\hat{d}_{s(i)}$ as the gradient increment. $\hat{d}_{s(1)} = \hat{\beta}_{s(1)}$, and $\hat{d}_{s(2)} = \hat{\beta}_{s(2)} - \hat{\beta}_{s(1)}$. The convexity constraint translates to the constraint that $\hat{d}_{s(i)} \geq 0$ for all $i > 1$.\\

$\hat{\beta}_{s(i)} = \sum_{j \leq i} \hat{d}_{s(i)}$.

\[
\hat{f}_s(x_{s(2)}) = \hat{f}_s(x_{s(1)}) + \hat{d}_{s(1)} ( x_{s(2)} - x_{s(1)})
\]

\begin{align*}
\hat{f}_s(x_{s(3)}) &= \hat{f}_s(x_{s(2)}) + \hat{\beta}_{s(2)} ( x_{s(3)} - x_{s(2)}) \\
 &= \hat{f}_s({x_{s(1)}}) + \hat{d}_{s(1)} ( x_{s(2)} - x_{s(1)}) + (\hat{d}_{s(2)}+\hat{d}_{s(1)}) (x_{s(3)} - x_{s(2)}) \\
 &= \hat{f}_s({x_{s(1)}}) + \hat{d}_{s(1)} (x_{s(3)}-x_{s(1)} ) + \hat{d}_{s(2)} (x_{s(3)}-x_{s(2)} )
\end{align*}

\[
\hat{f}_s(x_{s(i)}) = \hat{f}_s({x_{s(1)}}) +\hat{d}_{s(1)} ( x_{s(i)} - x_{s(1)}) + \hat{d}_{s(2)} ( x_{s(i)} - x_{s(2)}) + ... + \hat{d}_{s(i-1)} ( x_{s(i)} - x_{s(i-1)})
\]

Define $\Delta(j, x_{si}) = 0$ if $\trm{order}(i) \leq j$, $x_{si} - x_{s(j)}$ else. The $j$ ranges from $1$ to $n-1$. With this definition, we can re-write

\[
\hat{f}_s(x_{si}) = \hat{d}_{s}^\tran \Delta(x_{si}) \qquad \trm{where $\Delta(x_{si}) \in \R^{n-1}$.}
\]

With the simple constraint that all $\hat{d}_{si} \geq 0$ for $i > 1$.\\

\begin{align}
\min_{\{d_k, c_k\}}& \frac{1}{2n} \| Y - \sum_{k=1}^p ( \Delta_k d_k - c_k \mathbf{1}_n) \|_2^2 + \lambda_n \sum_{k=1}^p \| d_k \|_1 & \label{opt:alternate_opt} \\
\trm{s.t. $\forall k$, }  & d_{k2}, ..., d_{k(n-1)} \geq 0 	\qquad &\trm{(convexity)} \nonumber \\ 
	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	\qquad &\trm{(centering)} \nonumber \\
	& -B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n  \qquad &\trm{(boundedness*)} \nonumber \\
	& \|d_k\|_1 \leq L & \trm{(smoothness*)} \nonumber
\end{align}

@@

\begin{align}
\min_{\{d_k, c_k\}}& \frac{1}{2n} \| Y - \sum_{k \in S} ( \Delta_k d_k - c_k \mathbf{1}_n) \|_2^2 + \lambda_n \sum_{k=1}^p \| d_k \|_1 & \label{opt:restricted_alternate_opt} \\
\trm{s.t. $\forall k \in S$, }  & d_{k2}, ..., d_{k(n-1)} \geq 0 	\qquad &\trm{(convexity)} \nonumber \\ 
	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	\qquad &\trm{(centering)} \nonumber \\
	& -B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n  \qquad &\trm{(boundedness*)} \nonumber \\
	& \|d_k\|_1 \leq L & \trm{(smoothness*)} \nonumber
\end{align}

@@

Suppose
\[
\lambda \mathbf{1} > |\frac{1}{n} \Delta_k^\tran\hat{r}|,
\]
then we easily see that the first coordinate of $\mathbf{u}$ can be set to some value in $(-1,1)$ and $\mu_{k,i} > 0$ for $i=2,...,n$. Because we have strict inequality, Lemma [TODO:get wainwright lemma] shows that all solutions must be zero on $S^c$.
\end{proof}

@@

\begin{theorem} (Probabilistic: Controlling False Positives) \\
Suppose assumptions A1, A2, A3 hold. Suppose also that we run optimization~\ref{opt:alternate_opt} with the $B$-boundness constraint.

Suppose $\lambda_n \geq c b (sB + \sigma) \sqrt{ \frac{s}{n} \log n \log (pn)}$, then with probability at least $ 1 - \frac{C}{n}$, for all $j,k$,
\[
\lambda_n >  | \frac{1}{n} \hat{r}^\tran \Delta_{k,j}|
\]
And therefore, the solution to the optimization~\ref{opt:alternate_opt}, with boundedness constraint, is zero on $S^c$.
\end{theorem}

@@

\begin{theorem} (Probabilistic: Controlling False Negatives)\\
Suppose assumptions A1', A2', A3 hold. Suppose we run optimization~\ref{opt:alternate_opt} with both the $B$-boundedness and $L$-Lipschitz constraint. Suppose $f_0$ depends on all $s$-variables.

>>>>

\textbf{Setting:}
\begin{packed_enum}
\item Let $Y' = f_0(X) + \epsilon$ where $f_0$ is the true function and $\epsilon$ is noise.  Given $n$ samples $Y'_1,...,Y'_n$, we input into our optimization $Y = Y' - \bar{Y}'$.
\item Let $\mathcal{X} = [-b, b]^p$. Let $\mathcal{P}$ be a distribution on $\mathcal{X}$with positive density $p$. Let $X^{(1)},..., X^{(n)} $ be independent samples from $\mathcal{P}$. 
\item Let $s \leq p$ be a positive integer and let $S = \{1,...,s\}$ denote the set of relevant variables, that is, $f_0(X) = f_0(X_S)$.
\item Let $f_{01},...,f_{0s} \coloneqq \argmin_{f_1,...,f_s} \E(f_0(X) - \sum_{k\in S} f_k(X_k))^2$ be the population optimal additive components
\end{packed_enum}

\textbf{Assumptions:}
\begin{packed_enum}
\item[A1] Suppose that $X_S, X_{S^c}$ are independent.
\item[A1'] Suppose A1 is true and $\{ X_k \}_{k \in S}$ are all independent. 
\item[A2] Suppose that $\|f_0\|_\infty \leq sB$.
\item[A2'] Suppose that A2 is true and $f_0$ is convex and $L$-$Lipschitz$.
\item[A3] Suppose $\epsilon$ is mean-zero subgaussian, independent of $X$, with subgaussian scale $\sigma$.
\item[A4] Suppose that, for all $k\in S$, $\E(f_{0k}(X_k))^2 \geq \alpha$ for some constant $\alpha > 0$.  
\end{packed_enum}

@@

\begin{align}
\min_{\{d_k, c_k\}}& \frac{1}{2n} \| Y - \sum_{k=1}^p ( \Delta_k d_k - c_k \mathbf{1}_n) \|_2^2 + \lambda_n \sum_{k=1}^p \| d_k \|_1 & \label{opt:alternate_opt} \\
\trm{s.t. $\forall k$, }  & d_{k2}, ..., d_{k(n-1)} \geq 0 	\qquad &\trm{(convexity)} \nonumber \\ 
	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	\qquad &\trm{(centering)} \nonumber \\
	& -B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n  \qquad &\trm{(boundedness*)} \nonumber \\
	& \|d_k\|_1 \leq L & \trm{(smoothness*)} \nonumber\\
\end{align}

@@

\begin{align}
\min_{\{d_k, c_k\}}& \frac{1}{2n} \| Y - \sum_{k \in S} ( \Delta_k d_k - c_k \mathbf{1}_n) \|_2^2 + \lambda_n \sum_{k=1}^p \| d_k \|_1 & \label{opt:restricted_alternate_opt} \\
\trm{s.t. $\forall k \in S$, }  & d_{k2}, ..., d_{k(n-1)} \geq 0 	\qquad &\trm{(convexity)} \nonumber \\ 
	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	\qquad &\trm{(centering)} \nonumber \\
	& -B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n  \qquad &\trm{(boundedness*)} \nonumber \\
	& \|d_k\|_1 \leq L & \trm{(smoothness*)} \nonumber\\ 
\end{align}

@@

Suppose
\[
\lambda \mathbf{1} > |\frac{1}{n} \Delta_k^\tran\hat{r}|,
\]
then we easily see that the first coordinate of $\mathbf{u}$ can be set to some value in $(-1,1)$ and $\mu_{k,i} > 0$ for $i=2,...,n$. We need strict inequality to argue that all solutions are sparse. 
\end{proof}

@@

\begin{theorem} (Probabilistic: Controlling False Positives) \\
Suppose assumptions A1, A2, A3 hold.

Suppose $\lambda_n \geq c b (sB + \sigma) \sqrt{ \frac{s}{n} \log n \log (pn)}$, then with probability at least $ 1 - \frac{C}{n}$, for all $j,k$,
\[
\lambda_n >  | \frac{1}{n} \hat{r}^\tran \Delta_{k,j}|
\]
And therefore, the solution to the optimization~\ref{opt:alternate_opt} is zero on $S^c$.
\end{theorem}

@@

\begin{theorem} (Probabilistic: Controlling False Negatives)\\
Suppose assumptions A1', A2', A3 hold. Suppose $f_0$ depends on all $s$-variables.
